Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-18 paper/icml_drau/intro.tex

A time discretization invariant algorithm should in particular admit a
continuous-time
limit when the discretization timestep goes to $0$.  This
leads to precise design choices in term of agent architecture, exploration
policy, and learning rates scalings.  The resulting algorithm is shown to
provide better invariance to time discretization on many environments than
vanilla DQN or DDPG (Sec.~\ref{sec:exp}).  On a new environment, as soon as the
order of magnitude of the time discretization is known, our analysis readily
provides relevant scalings for a number of hyperparameters.

>>>>

A time discretization invariant algorithm should in particular admit a
continuous-time
limit when the discretization timestep goes to $0$.  This
leads to precise design choices in term of agent architecture, exploration
policy, and learning rates scalings.  The resulting algorithm is shown to
provide better invariance to time discretization than
vanilla DQN or DDPG, on many environments (Sec.~\ref{sec:exp}).  On a new environment, as soon as the
order of magnitude of the time discretization is known, our analysis readily
provides relevant scalings for a number of hyperparameters.
